---
title: "Statistical Inference Project"
author: "Greta Garcia"
date: "11/12/2022"
output: pdf_document
---

```{r lybraries, warning=FALSE, echo=FALSE}
library(ggplot2)
```

## A simulation exercise

**Show the sample mean and compare it to the theoretical mean of the distribution**
```{r mean, echo=TRUE}
lambda <- 0.2
smn <- mean(rexp(40, lambda))
mn <- 1/lambda

compMeans <- data.frame(Types=c("Sample Mean", "Theorical Mean"), 
                        Values=c(smn, mn))
p <- ggplot(data=compMeans, aes(x=Types, y=Values)) +
        geom_bar(stat="identity", fill="steelblue", width=0.5) +
        ggtitle("Compare Means")
```

**Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.**
```{r variances, echo=TRUE}
svariance <- var(rexp(40, lambda))
variance <- mn^2

compVariance <- data.frame(Types=c("Sample Variance", "Theorical Variance"), 
                           Values=c(svariance, variance))
p <- ggplot(data=compVariance, aes(x=Types, y=Values)) +
        geom_bar(stat="identity", fill="steelblue", width=0.5) +
        ggtitle("Compare Variances")
```

**Show that the distribution is approximately normal**
```{r graphicData, echo=TRUE}
random <- rexp(runif(1000), lambda)
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(runif(40), lambda)))
```

Draw graphics on the same pane to compare them and add a Normal of the Distribution to see if it's similar or not. To draw the normal, we calculate the  mean and the standard Deviation of the sample.
```{r graphicNormal, echo=TRUE}
par(mfrow=c(1,2))
hist(random, prob=TRUE, main="Exponential Distribution", 
     xlab="Random exponentials", col = "lightblue")
x <- seq(min(random), max(random), length = 40)
f <- dnorm(x, mean = mean(random), sd = sd(random))
lines(x, f, col = "red", lwd = 2)

hist(mns, prob=TRUE, main="Averages exponentials", 
     xlab="Averages", col = "lightblue")
x <- seq(min(mns), max(mns), length = 40)
f <- dnorm(x, mean = mean(mns), sd = sd(mns))
lines(x, f, col = "red", lwd = 2)
```
The Means distribution of a random sample of enough variables create a Normal Distribution for the Central Limit Theorem and in this exercise we have a demostration of this Theorem.

## Basic inferential data analysis

**Load the ToothGrowth data and perform some basic exploratory data analyses**
```{r exploratory, echo=TRUE}
tg <- ToothGrowth
str(tg)
```

**Provide a basic summary of the data.**
```{r summary, echo=TRUE}
summary(tg)
```

**Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose**

For Central limit Theorem we know that the means of this sample have a Normal distribution.
```{r splitSupp, echo=TRUE}
tg_oj <- tg[tg$supp=="OJ",]
tg_vc <- tg[tg$supp=="VC",]
```

In all cases, variables are Paired and supose that variances are equal
* H0: alpha1 = alpha2
* Ha: alpha1 != alpha2
```{r ttestSupp, echo=TRUE}
t.test(tg_oj$len, tg_vc$len, paired=TRUE, var.equal=TRUE)
```

```{r splitDose, echo=TRUE}
v_dose <- unique(tg$dose)
tg_supp1 <- tg[tg$dose==v_dose[1],]
tg_supp2 <- tg[tg$dose==v_dose[2],]
tg_supp3 <- tg[tg$dose==v_dose[3],]
```

```{r ttesDose, echo=TRUE, results="hide"}
t.test(tg_supp1$len, tg_supp2$len, paired=TRUE, var.equal=TRUE)
t.test(tg_supp1$len, tg_supp3$len, paired=TRUE, var.equal=TRUE)
t.test(tg_supp2$len, tg_supp3$len, paired=TRUE, var.equal=TRUE)
```

**State your conclusions and the assumptions needed for your conclusions**
We deny H0 because:
* Statistic t is equal to 3.3026 so is greater than quartile t at 95% (1.75305)
* p-value is 0.00255 so is lower than 5%
In conclusion mean from supp OJ is different than mean from supp VC with a 
Type I error lower than 5%.
